My Publication Title --- Single Author

### 2025-07-16 paper/quarto_aaai/paper.tex
asterisks added and rerendered

\caption{\label{tbl-main}Key performance metrics and bootstrapped
\emph{two} standard errors for all datasets. \textbf{Plausibility}
(columns 1-2): percentage reduction in implausibility for \(\text{IP}\)
and \(\text{IP}^*\), respectively; \textbf{Actionability} (column 3):
percentage reduction in costs with protected features. \textbf{Accuracy}
(columns 4-7): test accuracies and robust accuracies (\(\text{Acc}^*\))
for CT and the baseline (BL). Counterfactual outcomes in columns 1-3 are
aggregated across bootstrap samples and varying degrees of the energy
penalty \(\lambda_{\text{egy}}\) used for \emph{ECCo} at test time.
Standard errors for accuracy are bootstrapped from the test set.}

>>>>

\caption{\label{tbl-main}Key performance metrics and bootstrapped
standard errors (omitted if essentially zero) for all datasets.
\textbf{Plausibility} (columns 1-2): percentage reduction in
implausibility for \(\text{IP}\) and \(\text{IP}^*\), respectively;
\textbf{Actionability} (column 3): percentage reduction in costs with
protected features. \textbf{Accuracy} (columns 4-7): test accuracies and
robust accuracies (\(\text{Acc}^*\)) for CT and the baseline (BL).
Counterfactual outcomes in columns 1-3 are aggregated across bootstrap
samples and varying degrees of the energy penalty
\(\lambda_{\text{egy}}\) used for \emph{ECCo} at test time. Asterisks
(\(^*\)) in columns 1-3 indicate that difference is statistically
significant at 1\%-level. Standard errors for accuracy are bootstrapped
from the test set.}
